Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-06-16 analysis/memo2_TAS_reviewers.Rmd
further responses to review comments

This memorandum replies to comments from the TAS editor, a TAS associate editor, and a reviewer received in May 2023.

@@

@@

@@

Done.

@@

We have now provided links to the app as well as the code used to generate the results. Instructions for using the app are now provided not only in section 3.2 of the paper and the Supplemental Materials, but also a vignette in the app itself.

@@

@@

@@

@@

>>>>

This memorandum replies to comments received in May 2023 from the TAS editor, a TAS associate editor, and a reviewer.

@@

We have moved Figure 3 to the supplement.

@@

We have revised the figures accordingly.  To make the labels more readable, we used a lighter color for them.  We also fixed the reference to $b_curr$.

@@

We have revised accordingly. [TBD]

@@

We have now provided links to the app as well as the code used to generate the simulation results. Instructions for using the app are now provided not only in section 3.2 of the paper and the Supplemental Materials, but also a vignette in the app itself [TBD].

@@

As we discuss in the paper (page X, lines YY-YY), how one chooses the subsetting criteria (e.g., "similar" cases) would have to be justified with respect to its _assumed_ effect on the degree of compatability between the historical trials and the current trial ($b_hist - $b_curr$). We stress _assumed_, because outside simulations like ours, neither $b_hist$ nor $b_curr$ are directly observable in actual cases. Accordingly, for any subset of the historical strike data one chooses, our guidance for choosing an $\alpha$ value remains the same: Check for how sensitive to the posterior estimate of strike bias to different values of $\alpha$.  The current version of the software prototype does not contain a feaure that lets users subset the historical data by some characteristic (e.g., date, defendant race). The app, however, in principle, could be modified to add that kind of subsetting feature as a step prior to estimating the posterior distribution for bias.

@@

Thank you for this comment.  We have revised the paper accordingly.

@@

Thank you for catching that. We have revised the paper accordingly.

@@

Thank you for this comment.  We have revised the Discussion to discuss this further. [TBD].

First, we agree that high incompatbility may lead to error in bias detection. The challenge is that high incompatibility (in the case where $b_curr = 0$ or where $b_hist = 0$) is not directly observable.  This is why we recommend using sensitivity to choice of $\alpha$ value to ascertain whether to worry about high incompatability.

Second, we wish to address the idea that a judge may be reluctant to "seriously entertain a Batson challenge" if the strikes in the present case indicate essential equal "removal rates of protected and unprotected members of the venire." As an initial matter, we take "seriously entertain" to denote the premise that judge would be less likely to find a _Batson_ prima facie case and ultimately find a _Batson_ violation, given those removal rates. We do not dispute that premise about judges are likely to do.  We d
